Capstone Movielens Report

### 2025-11-29 reports/capstone-movielens.site/02.5.UME-model.Rmd

@@

@@

Now, we can refine our _User+Movie Effect Model_ by retraining on the entire `edx` dataset with the best value of the $\lambda$ parameter we just figured out (let's call it *Regularized User+Movie Effect Model*), for the definitive _RMSE_ calculation and use in subsequent models.
```{r, eval=FALSE}
best_result <- UME.rglr.fine_tune.results$best_result
UME.rglr.best_lambda <- best_result["param.best_value"]

@@

```{r}
```

```{r, echo=FALSE}
writeLines("*** The Best Fine-tuning Results ***")
```
```{r}
UME.rglr.fine_tune.results$best_result
```

```{r, echo=FALSE}
writeLines("*** Regularized User+Movie Effect Structure ***")
```
```{r}
str(rglr.UM_effect)

print_log1("Regularized User+Movie Effect Model has been re-trained for the best `lambda`: %1.",
         UME.rglr.best_lambda)
```

Finally, we calculate the *RMSE* for the ultimately *Regularized User+Movie Effect Model* and add the definitive result to our _Result Table_:
```{r, eval=FALSE}
UME.rglr.retrain.RMSE <- calc_user_movie_effect_RMSE.cv(rglr.UM_effect)
```
```{r}
print_log1("The best RMSE after being regularized: %1",
         UME.rglr.retrain.RMSE)
```
```{r, eval=FALSE}
RMSEs.ResultTibble.rglr.UME <- RMSEs.ResultTibble.UME |> 
  RMSEs.AddRow("Regularized User+Movie Effect Model", 
               UME.rglr.retrain.RMSE,
               comment = "Computed for `lambda` = %1" |>
                 msg.glue(UME.rglr.best_lambda))
```
```{r}
RMSE_kable(RMSEs.ResultTibble.rglr.UME)
```

@@

>>>>

::: {.noteblock data-latex=""}
The complete source code of the _User+Movie Effect_ computation described in this section is available in the [UME Model Building](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/capstone-movielens.main.R#L456) section of the [capstone-movielens.main.R](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/capstone-movielens.main.R#L456) script on _GitHub_.
:::

@@

::: {.noteblock data-latex=""}
The complete version of the source code provided in this section can be found in the [UME Model Regularization](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/capstone-movielens.main.R#L526) section of the [capstone-movielens.main.R](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/capstone-movielens.main.R#L526) script.
:::

@@

Now, we can refine our _User+Movie Effect Model_ by retraining on the entire `edx` dataset with the best value of the $\lambda$ parameter we just figured out (let's call it *Regularized User+Movie Effect Model* or *Regularized UME Model* for short), for the definitive _RMSE_ calculation and use in subsequent models:
```{r, eval=FALSE}
best_result <- UME.rglr.fine_tune.results$best_result
UME.rglr.best_lambda <- best_result["param.best_value"]

@@

```{r, echo=FALSE}
writeLines("*** The Best UM Effect Fine-tuning Results ***")
```
```{r}
UME.rglr.fine_tune.results$best_result
```

```{r, echo=FALSE}
writeLines("*** Regularized UM Effect Structure ***")
```
```{r}
str(rglr.UM_effect)

print_log1("Regularized UME Model has been re-trained for the best `lambda`: %1.",
         UME.rglr.best_lambda)
```

Finally, we calculate the *RMSE* for the ultimately *Regularized UME Model* and add the definitive result to our _Result Table_:
```{r, eval=FALSE}
UME.rglr.retrain.RMSE <- calc_user_movie_effect_RMSE.cv(rglr.UM_effect)
```
```{r}
print_log1("The best RMSE for the UME Model after being regularized: %1",
         UME.rglr.retrain.RMSE)
```
```{r, eval=FALSE}
RMSEs.ResultTibble.rglr.UME <- RMSEs.ResultTibble.UME |> 
  RMSEs.AddRow("Regularized User+Movie Effect Model", 
               UME.rglr.retrain.RMSE,
               comment = "Computed for `lambda` = %1" |>
                 msg.glue(UME.rglr.best_lambda))
```
```{r}
RMSE_kable(RMSEs.ResultTibble.rglr.UME)
```

@@

  - [calc_user_movie_effect_RMSE.cv](#func.calc_user_movie_effect_RMSE.cv) (described in the *Models Training: Support Functions /* [UME Model: Utility Functions] section) to calculate the *RMSE* for the *UME Model*;

### 2025-11-29 reports/capstone-movielens.site/02.6.UMGE-model.Rmd

@@

@@

Now, we can calculate the _Regularized UMG Effect_ by retraining our model on the entire `edx` dataset with the best value of the $\lambda$ parameter we just calculated, for the definitive _Root Mean Squared Error_ calculation and use in subsequent models.
```{r, eval=FALSE}
  best_result <- UMGE.rglr.fine_tune.results$best_result
  # param.best_value        best_RMSE 
  #     0.03554688       0.87297303

  UMGE.rglr.best_lambda <- best_result["param.best_value"]
  UMGE.rglr.best_RMSE <- best_result["best_RMSE"]

  put_log1("Re-training Regularized User+Movie+Genre Effect Model for the best `lambda`: %1...",
           UMGE.rglr.best_lambda)

  rglr.UMG_effect <- edx.sgr |> train_user_movie_genre_effect(UMGE.rglr.best_lambda)
```
```{r}
str(rglr.UMG_effect)
```

::: {.noteblock data-latex=""}
The complete version of the source code provided in this section are available in the [Re-training Regularized UMG Effect Model for the best $\lambda$](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/capstone-movielens.main.R#L910) section of the [capstone-movielens.main.R](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/capstone-movielens.main.R#L910) script on _GitHub_.
:::

We calculate the _Root Mean Squared Error_ for the ultimately computed _UMG Effect_ using [calc_UMG_effect_RMSE.cv](#func.calc_UMG_effect_RMSE.cv) function described above as follows:
```{r, eval=FALSE}
  rglr.UMG_effect.RMSE <- calc_user_movie_genre_effect_RMSE.cv(rglr.UMG_effect)
```
```{r, echo=FALSE}
  print_log2("Regularized User+Movie+Genre Effect RMSE has been computed for the best `lambda = %1`: %2.",
           UMGE.rglr.best_lambda,
           rglr.UMG_effect.RMSE)
```

Finally, we add the definitive result for the current model to our _Result Table_:
```{r, eval=FALSE}
RMSEs.ResultTibble.rglr.UMGE <- RMSEs.ResultTibble.UMGE |> 
  RMSEs.AddRow("Regularized User+Movie+Genre Effect Model", 
               rglr.UMG_effect.RMSE,
               comment = "Computed for `lambda` = %1" |>
                 msg.glue(UMGE.rglr.best_lambda))
```
```{r}
RMSE_kable(RMSEs.ResultTibble.rglr.UMGE)
```

::: {.noteblock data-latex=""}
Here use the [RMSEs.AddRow](#func.RMSEs.AddRow) and [RMSE_kable](#func.RMSE_kable) functions described in the [Result RMSEs Tibble Functions] section of [Appendix A: Support Functions].
:::

>>>>

::: {.noteblock data-latex=""}
The complete source code of the _User+Movie+Genre Effect_ computation described in this section is available in the [User+Movie+Genre Effect (UMGE) Model](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/capstone-movielens.main.R#L730) section of the [capstone-movielens.main.R](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/capstone-movielens.main.R#L730) script on _GitHub_.
:::

@@

::: {.noteblock data-latex=""}
The complete version of the source code provided in this section can be found in the [UMGE Model Regularization](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/capstone-movielens.main.R#L948) section of the [capstone-movielens.main.R](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/capstone-movielens.main.R#L948) script.
:::

@@

::: {.noteblock data-latex=""}
The complete version of the source code provided in this section are available in the [UMGE Model Regularization: Re-training with the best `lambda`](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/capstone-movielens.main.R#L1062) section of the [capstone-movielens.main.R](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/capstone-movielens.main.R#L1062) script on _GitHub_.
:::

Now, we can refine our _User+Movie+Genre Effect Model_ by retraining on the entire `edx` dataset with the best value of the $\lambda$ parameter we just figured out (let's call it *Regularized User+Movie+Genre Effect Model* or *Regularized UMGE Model* for short), for the definitive _RMSE_ calculation and use in subsequent models:
```{r, eval=FALSE}
  best_result <- UMGE.rglr.fine_tune.results$best_result
  UMGE.rglr.best_lambda <- best_result["param.best_value"]
#  UMGE.rglr.best_RMSE <- best_result["best_RMSE"]

  rglr.UMG_effect <- edx.sgr |> train_user_movie_genre_effect(UMGE.rglr.best_lambda)
```

::: {.noteblock data-latex=""}
In the code snippet above we use the [train_user_movie_genre_effect](#func.train_user_movie_genre_effect) function described in the *Models Training: Support Functions /* [UME Model: Utility Functions] section of [Appendix A: Support Functions].
:::

```{r, echo=FALSE}
writeLines("*** The Best UMG Effect Fine-tuning Results ***")
```
```{r}
UMGE.rglr.fine_tune.results$best_result
```

```{r, echo=FALSE}
writeLines("*** Regularized UMG Effect Structure ***")
```
```{r}
str(rglr.UMG_effect)

print_log1("Regularized UMGE Model has been re-trained for the best `lambda`: %1.",
         UMGE.rglr.best_lambda)
```

Finally, we calculate the *RMSE* for the ultimately *Regularized UMGE Model* and add the definitive result to our _Result Table_:
```{r, eval=FALSE}
  rglr.UMG_effect.RMSE <- calc_user_movie_genre_effect_RMSE.cv(rglr.UMG_effect)
```
```{r}
print_log1("The best RMSE for the UME Model after being regularized: %1",
         rglr.UMG_effect.RMSE)
```
```{r, eval=FALSE}
RMSEs.ResultTibble.rglr.UMGE <- RMSEs.ResultTibble.UMGE |> 
  RMSEs.AddRow("Regularized User+Movie+Genre Effect Model", 
               rglr.UMG_effect.RMSE,
               comment = "Computed for `lambda` = %1" |>
                 msg.glue(UMGE.rglr.best_lambda))
```
```{r}
RMSE_kable(RMSEs.ResultTibble.rglr.UMGE)
```

  - [calc_UMG_effect_RMSE.cv](#func.calc_UMG_effect_RMSE.cv) (described in the *Models Training: Support Functions /* [UMGE Model: Utility Functions] section) to calculate the *RMSE* for the *UMGE Model*;
